\documentclass[12pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{daves,fancyhdr,natbib,graphicx,dcolumn,amsmath,lastpage,url}
\usepackage{amsmath,amssymb,epstopdf,longtable}
\usepackage{paralist}  % need to properly formulate standard answer blocks
\usepackage[final]{pdfpages}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\pagestyle{fancy}
\lhead{CE 3305 Fluid Mechanics; Exercise Set 0}
\rhead{Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}
\lfoot{REVISION A}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}
\renewcommand\headrulewidth{0pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begingroup
\begin{center}
{\textbf{{ CE 3305 Engineering Fluid Mechanics} \\ Exercise Set 0 \\ Summer 2018 -- GERMANY} }
\end{center}
\endgroup
\begingroup
~\newline
\textbf{Purpose}: Demonstrate use of the on-line course resources and ability to upload assignments back to the learning management system.\\
\textbf{Assessment Criteria}: Completion score based on successful upload to class learning management system, and correct plot result in item 4 below.\\~\\
\textbf{Exercises}
\begin{enumerate}
\item Visit the course umbrella website \url{http://theodore-macbookpro.ttu.edu/} and screen capture the June 20, 2018 post.
\item Take the link on the right margin index to the RTFM Learning Management Site \url{http://theodore-macbookpro.ttu.edu/moodle/} and screen capture the entry page.  It may issue a password challenge, in which case meet the challenge and capture an image of the first content screen
\item Visit the on-line toolkit \url{http://theodores-pro.ttu.edu/mytoolbox-server/} and use the toolkit (Fluid Mechanics Tools) to determine the density of water at 40-degrees celsius.  Screen capture the toolkit output.
\item Download and install \textbf{R} onto your laptop.  Generate a simple plot using the following script instructions:
\begin{verbatim}
x <- c(0,1,2,3,4,5)
y <- x^2
plot(x,y,type="s")
\end{verbatim}
\end{enumerate}
Collect all the above results into a single PDF document and upload the document with your name and team mate names on the document.    \footnote{Use this page (with your name added) as the cover sheet. File upload size is restricted to 8MB, so use reduced-file-size tools to meet this restriction.}

\end{document}  